Balsa: A Compact Line Notation Based on SMILES

### 2022-06-25 manuscript.tex
Updates figure deselection and selection.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{selection-and-deselection.pdf}
    \caption{Deselection and Selection. Deselection unsets the atomic selected flag with simultaneous promotion of matching bonds. Selection sets the atomic selected flag with simultaneous demotion of intervening single and double bonds to elided bonds.}
    \label{fig:selection-and-deselection}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{selection-and-deselection.pdf}
    \caption{Deselection and Selection. Deselection unsets the atomic selected flag (open circle) with simultaneous promotion of matching bonds. Selection sets the atomic selected flag (closed circle) with simultaneous demotion of intervening single and double bonds to elided bonds.}
    \label{fig:selection-and-deselection}
\end{figure}
